CP_MSSA

### 2025-03-12 Code/R/Research/CP_MSSA.Rmd
CP noise mixing

  rec <- lapply(Ls_cp, function(L)
    tens_mssa_reconstruct(
      x,
      L,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    ))
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

  rec <- list(
    mssa = reconstruct(ssa(x, L = L_mssa, kind = "mssa"), groups = groups_mssa),
    cp_mssa = tens_mssa_reconstruct(
      x,
      L_cp,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    ),
    ho_mssa = tens_mssa_reconstruct(
      x,
      L = L_ho,
      groups = groups_mssa,
      groups3 = groups3,
      decomp = "hooi",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    )
  )
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

max.r <- max(sapply(groups_mssa, max))

Ls_mssa <- seq(from = max.r,
               to = N - max.r + 1,
               by = 2)
Ls_cp <- seq(from = max.r,
             to = N - max.r + 1,
             by = 2)
# Ls_cp <- c(20, 40)
Ls_ho <- seq(from = max.r,
                 to = (N + 1) %/% 2,
                 by = 2)

@@

rmse_L_cpmssa_res <- t(rbind(Ls_cp, rmse_L_cpmssa(R)))
save(
  rmse_L_cpmssa_res,
  file = paste0(
    "./Research/comp_results/cpmssa_",
    save_file_name,
    "_L.RData"
  )
)
rmse_L_cpmssa_res[order(rowMeans(rmse_L_cpmssa_res[, -1]), decreasing = FALSE), ] |>
  head() |>
  print()
```

>>>>

  rec <- lapply(Ls_cp, function(L)
    tens_mssa_reconstruct(
      x,
      L,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      start = "svd"
    ))
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

  rec <- list(
    mssa = reconstruct(ssa(x, L = L_mssa, kind = "mssa"), groups = groups_mssa),
    cp_mssa = tens_mssa_reconstruct(
      x,
      L_cp,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      start = "svd"
    ),
    ho_mssa = tens_mssa_reconstruct(
      x,
      L = L_ho,
      groups = groups_mssa,
      groups3 = groups3,
      decomp = "hooi",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    )
  )
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

max.r <- max(sapply(groups_mssa, max))
max.rcp <- max(sapply(groups_cp, max))

Ls_mssa <- seq(from = max.r,
               to = N - max.r + 1,
               by = 2)
Ls_cp <- seq(from = max.rcp,
             to = N - max.rcp + 1,
             by = 2)
# Ls_cp <- c(20, 40)
Ls_ho <- seq(from = max.r,
                 to = (N + 1) %/% 2,
                 by = 2)

@@

rmse_L_cpmssa_res <- t(rbind(Ls_cp, rmse_L_cpmssa(R)))
# save(
#   rmse_L_cpmssa_res,
#   file = paste0(
#     "./Research/comp_results/cpmssa_",
#     save_file_name,
#     "_L.RData"
#   )
# )
rmse_L_cpmssa_res[order(rowMeans(rmse_L_cpmssa_res[, -1]), decreasing = FALSE), ] |>
  head() |>
  print()
# 62 1.139832 1.163155 1.211639 1.165164 1.210579 1.182345 1.168282 2.261075 2.241531
# 56 1.102377 1.134577 1.175887 1.130599 1.181898 1.151490 1.109888 2.002356 2.020384
```
